Comparing \pkg{binsegRcpp} with other implementations of binary segmentation for change-point detection

### 2025-05-06 figure-heap-refs-other.tex
direct label in tikz

% Created by tikzDevice version 0.12.6 on 2025-05-06 20:54:35
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (505.89,505.89);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,264.98) rectangle (262.59,483.82);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 46.86,264.98) rectangle (262.59,483.82);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,289.91) --
	(262.59,289.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,346.74) --
	(262.59,346.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,403.56) --
	(262.59,403.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,460.39) --
	(262.59,460.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 50.63,264.98) --
	( 50.63,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (109.85,264.98) --
	(109.85,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.08,264.98) --
	(169.08,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (228.30,264.98) --
	(228.30,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,318.33) --
	(262.59,318.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,375.15) --
	(262.59,375.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,431.98) --
	(262.59,431.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.24,264.98) --
	( 80.24,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.46,264.98) --
	(139.46,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.69,264.98) --
	(198.69,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.92,264.98) --
	(257.92,483.82);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 56.67,398.60) --
	( 74.50,286.74) --
	( 92.33,305.45) --
	(110.16,319.22) --
	(127.98,338.53) --
	(145.81,354.75) --
	(163.64,370.70) --
	(181.47,387.04) --
	(199.30,403.70) --
	(217.13,420.58) --
	(234.96,437.56) --
	(252.79,454.61);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 92.33,300.65) --
	(110.16,317.76) --
	(127.98,334.86) --
	(145.81,351.97) --
	(163.64,369.07) --
	(181.47,386.18) --
	(199.30,403.29) --
	(217.13,420.39) --
	(234.96,437.50) --
	(252.79,454.61);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 56.67,360.52) --
	( 74.50,369.07) --
	( 92.33,377.63) --
	(110.16,386.18) --
	(127.98,394.73) --
	(145.81,403.29) --
	(163.64,411.84) --
	(181.47,420.39) --
	(199.30,428.95) --
	(217.13,437.50) --
	(234.96,446.05) --
	(252.79,454.61);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,264.98) rectangle (262.59,483.82);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.10,297.80) --
	( 92.33,300.65) --
	(100.56,297.80) --
	(100.56,288.94) --
	( 84.10,288.94) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 50.68,297.80) --
	( 56.67,360.52) --
	( 62.66,297.80) --
	( 62.66,288.94) --
	( 50.68,288.94) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.33,290.92) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 56.67,290.92) {$N$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.86,264.98) rectangle (262.59,483.82);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (262.59,259.48);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 46.86, 40.64) rectangle (262.59,259.48);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 45.62) --
	(262.59, 45.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 88.17) --
	(262.59, 88.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,130.71) --
	(262.59,130.71);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,173.25) --
	(262.59,173.25);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,215.80) --
	(262.59,215.80);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,258.34) --
	(262.59,258.34);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 50.63, 40.64) --
	( 50.63,259.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] (109.85, 40.64) --
	(109.85,259.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.08, 40.64) --
	(169.08,259.48);

\path[draw=drawColor,line width= 0.3pt,line join=round] (228.30, 40.64) --
	(228.30,259.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 66.89) --
	(262.59, 66.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,109.44) --
	(262.59,109.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,151.98) --
	(262.59,151.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,194.52) --
	(262.59,194.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,237.07) --
	(262.59,237.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.24, 40.64) --
	( 80.24,259.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.46, 40.64) --
	(139.46,259.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.69, 40.64) --
	(198.69,259.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.92, 40.64) --
	(257.92,259.48);
\definecolor{drawColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,224.26) -- (262.59,224.26);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] ( 56.67, 66.89) --
	( 74.50, 78.17) --
	( 92.33, 71.00) --
	(110.16, 72.26) --
	(127.98, 68.86) --
	(145.81, 70.52) --
	(163.64, 78.50) --
	(181.47,112.13) --
	(199.30,141.19) --
	(217.13,167.33) --
	(234.96,193.27) --
	(252.79,228.18) --
	(252.79,227.94) --
	(234.96,192.75) --
	(217.13,155.33) --
	(199.30,123.25) --
	(181.47, 94.27) --
	(163.64, 70.55) --
	(145.81, 55.19) --
	(127.98, 53.93) --
	(110.16, 59.50) --
	( 92.33, 55.94) --
	( 74.50, 63.02) --
	( 56.67, 50.59) --
	cycle;

\path[] ( 56.67, 66.89) --
	( 74.50, 78.17) --
	( 92.33, 71.00) --
	(110.16, 72.26) --
	(127.98, 68.86) --
	(145.81, 70.52) --
	(163.64, 78.50) --
	(181.47,112.13) --
	(199.30,141.19) --
	(217.13,167.33) --
	(234.96,193.27) --
	(252.79,228.18);

\path[] (252.79,227.94) --
	(234.96,192.75) --
	(217.13,155.33) --
	(199.30,123.25) --
	(181.47, 94.27) --
	(163.64, 70.55) --
	(145.81, 55.19) --
	(127.98, 53.93) --
	(110.16, 59.50) --
	( 92.33, 55.94) --
	( 74.50, 63.02) --
	( 56.67, 50.59);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 56.67, 52.89) --
	( 74.50, 69.63) --
	( 92.33, 57.53) --
	(110.16, 60.50) --
	(127.98, 57.01) --
	(145.81, 58.85) --
	(163.64, 71.74) --
	(181.47, 94.98) --
	(199.30,125.79) --
	(217.13,156.20) --
	(234.96,192.85) --
	(252.79,228.05);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 74.50, 72.89) --
	( 92.33, 91.02) --
	(110.16,107.95) --
	(127.98,124.12) --
	(145.81,139.78) --
	(163.64,155.05) --
	(181.47,170.03) --
	(199.30,184.79) --
	(217.13,199.35) --
	(234.96,213.77) --
	(252.79,228.05);

\path[draw=drawColor,line width= 1.1pt,line join=round] (110.16, 74.37) --
	(127.98, 93.58) --
	(145.81,112.79) --
	(163.64,132.00) --
	(181.47,151.21) --
	(199.30,170.42) --
	(217.13,189.63) --
	(234.96,208.84) --
	(252.79,228.05);

\path[draw=drawColor,line width= 1.1pt,line join=round] (145.81, 74.37) --
	(163.64, 99.99) --
	(181.47,125.60) --
	(199.30,151.21) --
	(217.13,176.83) --
	(234.96,202.44) --
	(252.79,228.05);

\path[draw=drawColor,line width= 1.1pt,line join=round] (181.47, 74.37) --
	(199.30,112.79) --
	(217.13,151.21) --
	(234.96,189.63) --
	(252.79,228.05);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (262.59,259.48);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.83, 70.05) --
	( 74.50, 72.89) --
	( 93.17, 70.05) --
	( 93.17, 59.24) --
	( 55.83, 59.24) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.75, 70.05) --
	(110.16, 74.37) --
	(121.56, 70.05) --
	(121.56, 59.24) --
	( 98.75, 59.24) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.59, 70.05) --
	(145.81, 74.37) --
	(154.04, 70.05) --
	(154.04, 61.18) --
	(137.59, 61.18) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.24, 70.05) --
	(181.47, 74.37) --
	(189.70, 70.05) --
	(189.70, 61.18) --
	(173.24, 61.18) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 74.50, 63.16) {$N \log N$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (110.16, 63.16) {$N^{1.5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.81, 63.16) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.47, 63.16) {$N^3$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 46.86, 40.64) rectangle (262.59,259.48);
\end{scope}
\begin{scope}
\path[clip] (268.09,264.98) rectangle (483.82,483.82);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (268.09,264.98) rectangle (483.82,483.82);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.09,289.91) --
	(483.82,289.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.09,346.74) --
	(483.82,346.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.09,403.56) --
	(483.82,403.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.09,460.39) --
	(483.82,460.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] (272.36,264.98) --
	(272.36,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (326.65,264.98) --
	(326.65,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (380.94,264.98) --
	(380.94,483.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] (435.23,264.98) --
	(435.23,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.09,318.33) --
	(483.82,318.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.09,375.15) --
	(483.82,375.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (268.09,431.98) --
	(483.82,431.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.50,264.98) --
	(299.50,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.79,264.98) --
	(353.79,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (408.08,264.98) --
	(408.08,483.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (462.37,264.98) --
	(462.37,483.82);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (277.90,302.81) --
	(294.24,264.98) --
	(310.58,264.98) --
	(326.93,264.98) --
	(343.27,264.98) --
	(359.61,274.93) --
	(375.95,282.47) --
	(392.30,290.48) --
	(408.64,298.75) --
	(424.98,307.16) --
	(441.33,315.64) --
	(457.67,324.16) --
	(474.01,332.70);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (441.33,298.48) --
	(457.67,315.59) --
	(474.01,332.70);

\path[draw=drawColor,line width= 1.1pt,line join=round] (408.64,298.48) --
	(424.98,307.04) --
	(441.33,315.59) --
	(457.67,324.14) --
	(474.01,332.70);
\end{scope}
\begin{scope}
\path[clip] (268.09,264.98) rectangle (483.82,483.82);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (433.10,295.64) --
	(441.33,298.48) --
	(449.55,295.64) --
	(449.55,286.77) --
	(433.10,286.77) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (402.66,295.64) --
	(408.64,298.48) --
	(414.63,295.64) --
	(414.63,286.77) --
	(402.66,286.77) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (441.33,288.75) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (408.64,288.75) {$N$};
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.09,264.98) rectangle (483.82,483.82);
\end{scope}
\begin{scope}
\path[clip] (268.09, 40.64) rectangle (483.82,259.48);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (268.09, 40.64) rectangle (483.82,259.48);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (268.09, 45.62) --
	(483.82, 45.62);

>>>>

% Created by tikzDevice version 0.12.6 on 2025-05-06 22:53:33
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,120.44) rectangle (226.46,194.74);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 46.86,120.44) rectangle (226.46,194.74);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,125.99) --
	(226.46,125.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,145.23) --
	(226.46,145.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,164.47) --
	(226.46,164.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86,183.70) --
	(226.46,183.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 50.00,120.44) --
	( 50.00,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 99.30,120.44) --
	( 99.30,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (148.61,120.44) --
	(148.61,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.91,120.44) --
	(197.91,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,135.61) --
	(226.46,135.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,154.85) --
	(226.46,154.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,174.08) --
	(226.46,174.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,193.32) --
	(226.46,193.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 74.65,120.44) --
	( 74.65,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.95,120.44) --
	(123.95,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.26,120.44) --
	(173.26,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (222.56,120.44) --
	(222.56,194.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03,172.40) --
	( 69.87,134.54) --
	( 84.71,140.87) --
	( 99.55,145.53) --
	(114.40,152.07) --
	(129.24,157.56) --
	(144.08,162.96) --
	(158.92,168.49) --
	(173.77,174.13) --
	(188.61,179.84) --
	(203.45,185.59) --
	(218.29,191.36);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 84.71,139.25) --
	( 99.55,145.04) --
	(114.40,150.83) --
	(129.24,156.62) --
	(144.08,162.41) --
	(158.92,168.20) --
	(173.77,173.99) --
	(188.61,179.78) --
	(203.45,185.57) --
	(218.29,191.36);

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.03,159.51) --
	( 69.87,162.41) --
	( 84.71,165.30) --
	( 99.55,168.20) --
	(114.40,171.09) --
	(129.24,173.99) --
	(144.08,176.89) --
	(158.92,179.78) --
	(173.77,182.68) --
	(188.61,185.57) --
	(203.45,188.47) --
	(218.29,191.36);
\end{scope}
\begin{scope}
\path[clip] ( 46.86,120.44) rectangle (226.46,194.74);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.48,136.40) --
	( 84.71,139.25) --
	( 92.94,136.40) --
	( 92.94,127.54) --
	( 76.48,127.54) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 49.04,136.40) --
	( 55.03,159.51) --
	( 61.01,136.40) --
	( 61.01,127.54) --
	( 49.04,127.54) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 84.71,128.09) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 55.03,128.09) {$N$};
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (226.46,114.94);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 46.86, 40.64) rectangle (226.46,114.94);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 44.40) --
	(226.46, 44.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 71.59) --
	(226.46, 71.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 46.86, 98.78) --
	(226.46, 98.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 50.00, 40.64) --
	( 50.00,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 99.30, 40.64) --
	( 99.30,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] (148.61, 40.64) --
	(148.61,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] (197.91, 40.64) --
	(197.91,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 58.00) --
	(226.46, 58.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86, 85.19) --
	(226.46, 85.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.86,112.38) --
	(226.46,112.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 74.65, 40.64) --
	( 74.65,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.95, 40.64) --
	(123.95,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (173.26, 40.64) --
	(173.26,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (222.56, 40.64) --
	(222.56,114.94);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] ( 55.03, 58.00) --
	( 69.87, 61.60) --
	( 84.71, 59.31) --
	( 99.55, 59.71) --
	(114.40, 58.63) --
	(129.24, 59.16) --
	(144.08, 61.71) --
	(158.92, 72.45) --
	(173.77, 81.74) --
	(188.61, 90.10) --
	(203.45, 98.38) --
	(218.29,109.54) --
	(218.29,109.46) --
	(203.45, 98.22) --
	(188.61, 86.26) --
	(173.77, 76.01) --
	(158.92, 66.75) --
	(144.08, 59.17) --
	(129.24, 54.26) --
	(114.40, 53.86) --
	( 99.55, 55.64) --
	( 84.71, 54.50) --
	( 69.87, 56.76) --
	( 55.03, 52.79) --
	cycle;

\path[] ( 55.03, 58.00) --
	( 69.87, 61.60) --
	( 84.71, 59.31) --
	( 99.55, 59.71) --
	(114.40, 58.63) --
	(129.24, 59.16) --
	(144.08, 61.71) --
	(158.92, 72.45) --
	(173.77, 81.74) --
	(188.61, 90.10) --
	(203.45, 98.38) --
	(218.29,109.54);

\path[] (218.29,109.46) --
	(203.45, 98.22) --
	(188.61, 86.26) --
	(173.77, 76.01) --
	(158.92, 66.75) --
	(144.08, 59.17) --
	(129.24, 54.26) --
	(114.40, 53.86) --
	( 99.55, 55.64) --
	( 84.71, 54.50) --
	( 69.87, 56.76) --
	( 55.03, 52.79);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 55.03, 53.52) --
	( 69.87, 58.87) --
	( 84.71, 55.00) --
	( 99.55, 55.96) --
	(114.40, 54.84) --
	(129.24, 55.43) --
	(144.08, 59.55) --
	(158.92, 66.97) --
	(173.77, 76.82) --
	(188.61, 86.54) --
	(203.45, 98.25) --
	(218.29,109.50);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (129.24, 60.39) --
	(144.08, 68.57) --
	(158.92, 76.76) --
	(173.77, 84.94) --
	(188.61, 93.13) --
	(203.45,101.31) --
	(218.29,109.50);

\path[draw=drawColor,line width= 1.1pt,line join=round] (158.92, 60.39) --
	(173.77, 72.67) --
	(188.61, 84.94) --
	(203.45, 97.22) --
	(218.29,109.50);
\end{scope}
\begin{scope}
\path[clip] ( 46.86, 40.64) rectangle (226.46,114.94);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.01, 57.54) --
	(129.24, 60.39) --
	(137.47, 57.54) --
	(137.47, 48.68) --
	(121.01, 48.68) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.70, 57.54) --
	(158.92, 60.39) --
	(167.15, 57.54) --
	(167.15, 48.68) --
	(150.70, 48.68) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (129.24, 49.23) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (158.92, 49.23) {$N^3$};
\end{scope}
\begin{scope}
\path[clip] (231.96,120.44) rectangle (411.55,194.74);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (231.96,120.44) rectangle (411.55,194.74);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,125.99) --
	(411.55,125.99);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,145.23) --
	(411.55,145.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,164.47) --
	(411.55,164.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96,183.70) --
	(411.55,183.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] (235.51,120.44) --
	(235.51,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (280.70,120.44) --
	(280.70,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (325.90,120.44) --
	(325.90,194.74);

\path[draw=drawColor,line width= 0.3pt,line join=round] (371.10,120.44) --
	(371.10,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,135.61) --
	(411.55,135.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,154.85) --
	(411.55,154.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,174.08) --
	(411.55,174.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,193.32) --
	(411.55,193.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (258.11,120.44) --
	(258.11,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.30,120.44) --
	(303.30,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.50,120.44) --
	(348.50,194.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.69,120.44) --
	(393.69,194.74);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 2.3pt,line join=round] (240.12,139.98) --
	(253.73,120.44) --
	(267.33,120.44) --
	(280.94,120.44) --
	(294.54,120.44) --
	(308.15,130.54) --
	(321.75,133.09) --
	(335.36,135.80) --
	(348.96,138.60) --
	(362.57,141.45) --
	(376.17,144.32) --
	(389.78,147.21) --
	(403.39,150.09);
\definecolor{drawColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 1.1pt,line join=round] (376.17,138.51) --
	(389.78,144.30) --
	(403.39,150.09);

\path[draw=drawColor,line width= 1.1pt,line join=round] (348.96,138.51) --
	(362.57,141.41) --
	(376.17,144.30) --
	(389.78,147.20) --
	(403.39,150.09);
\end{scope}
\begin{scope}
\path[clip] (231.96,120.44) rectangle (411.55,194.74);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (367.95,135.67) --
	(376.17,138.51) --
	(384.40,135.67) --
	(384.40,126.80) --
	(367.95,126.80) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (342.98,135.67) --
	(348.96,138.51) --
	(354.95,135.67) --
	(354.95,126.80) --
	(342.98,126.80) --
	cycle;

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (376.17,127.36) {$N^2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (348.96,127.36) {$N$};
\end{scope}
\begin{scope}
\path[clip] (231.96, 40.64) rectangle (411.55,114.94);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (231.96, 40.64) rectangle (411.55,114.94);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 44.40) --
	(411.55, 44.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 71.59) --
	(411.55, 71.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (231.96, 98.78) --
	(411.55, 98.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (235.51, 40.64) --
	(235.51,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] (280.70, 40.64) --
	(280.70,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] (325.90, 40.64) --
	(325.90,114.94);

\path[draw=drawColor,line width= 0.3pt,line join=round] (371.10, 40.64) --
	(371.10,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 58.00) --
	(411.55, 58.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96, 85.19) --
	(411.55, 85.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.96,112.38) --
	(411.55,112.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (258.11, 40.64) --
	(258.11,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (303.30, 40.64) --
	(303.30,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (348.50, 40.64) --
	(348.50,114.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.69, 40.64) --
	(393.69,114.94);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.50] (240.12, 60.30) --
	(253.73, 64.90) --
	(267.33, 65.15) --
	(280.94, 69.28) --
	(294.54, 73.86) --
	(308.15, 75.13) --
	(321.75, 78.18) --
	(335.36, 83.17) --
	(348.96, 88.17) --
	(362.57, 93.25) --
	(376.17,101.77) --
	(389.78,104.80) --
	(403.39,111.56) --
	(403.39,111.28) --
	(389.78,104.61) --
	(376.17, 98.60) --
	(362.57, 93.17) --
	(348.96, 88.03) --
	(335.36, 83.04) --
	(321.75, 78.08) --
	(308.15, 73.15) --
	(294.54, 71.03) --
	(280.94, 68.63) --
	(267.33, 63.57) --
	(253.73, 60.00) --
	(240.12, 54.65) --
	cycle;
